Evolution of pre-copulatory and post-copulatory strategies of inbreeding avoidance

### 2017-07-28 ms_pre_post.Rmd
Minor edits

For example, @Pomiankowski1987 identified four costs categories relevant to mating frequency and mate choice, including elevated risks of predation or disease transmission, and time or energey expenditure. For example, polyandrous females might experience increased risk of disease transmission [@Roberts2015]. This cost would more realistically apply to a female's realised number of mates rather than her tendency for polyandry. Polyandrous females might also risk harm caused by sexual conflict over multiple mating [e.g., @Arnqvist2005; @Parker2006]. Inbreeding theory predicts that males should be more tolerant of inbreeding than females, leading to sexual conflict over inbreeding in mating encounters [@Parker1979; @Parker2006; @Kokko2006; @Duthie2015a]. Future models could therefore explicitly consider sexual conflict over both polyandry and pre-copulatory inbreeding, and hence capture internally-consistent mechanistic costs. Further, sexual conflict might also affect post-copulatory inbreeding. For example, when female guppies (*Poecilia reticulata*) were artificially inseminated with equal quantitites of sperm from full-siblings and unrelated males, more eggs were fertilised by unrelated males because the velocities of full sibling's sperm were reduced by females' ovarian fluids [@Gasparini2011]. In black field crickets (*Teleogryllus commodus*), females attempt to remove the spermatophores of unwanted males after copulation, and are capable of controlling sperm transfer to spermatheca after copulation occurs [@Bussiere2006; @Tuni2013].

We restricted our model to simulate how evolution of traits was affected by their direct costs and indirect benefits due to inbreeding avoidance. Although natural populations will include additional beneficial traits that might affect evolution of mating strategies, targeting our focus on traits affecting inbreeding and polyandry allows us to better isolate their effects and therefore better develop general hypotheses. Future models could be further developed to include additional benefits and costs of reproductive strategies, and benefit and cost values could be parameterised using data from empirical populations, hence facilitating more quantitative predictions for specific systems. The addition of such mechanistic detail, and the inclusion of data from populations of interest to parameterise model extensions, could ultimately improve understanding and prediction of reproductive strategy evolution and thereby link theory, modelling, and empirical hypothesis testing.

>>>>

For example, @Pomiankowski1987 identified four costs categories relevant to mating frequency and mate choice, including elevated risks of predation or disease transmission, and time or energey expenditure. For example, polyandrous females might experience increased risk of disease transmission [@Roberts2015]. This cost would more realistically apply to a female's realised number of mates rather than her tendency for polyandry. Polyandrous females might also risk harm caused by sexual conflict over multiple mating [e.g., @Arnqvist2005; @Parker2006]. Inbreeding theory predicts that males should be more tolerant of inbreeding than females, leading to sexual conflict over inbreeding in mating encounters [@Parker1979; @Parker2006; @Kokko2006; @Duthie2015a]. Future models could therefore explicitly consider sexual conflict over both polyandry and pre-copulatory inbreeding, and hence capture internally-consistent mechanistic costs. Further, sexual conflict might also affect post-copulatory inbreeding. For example, when female guppies (*Poecilia reticulata*) were artificially inseminated with equal quantitites of sperm from full-siblings and unrelated males, more eggs were fertilised by unrelated males because the velocities of full sibling's sperm were reduced by females' ovarian fluids [@Gasparini2011]. In black field crickets (*Teleogryllus commodus*), females attempt to remove the spermatophores of unwanted males after copulation, and are capable of controlling sperm transfer to spermatheca after copulation occurs [@Bussiere2006; @Tuni2013]. Model extensions might therefore incorporate such post-copulatory sexual conflict to better understand female and male reproductive strategy evolution.

We restricted our model to simulate how evolution of traits was affected by their direct costs and indirect benefits due to inbreeding avoidance. Although natural populations will include additional beneficial traits that might affect evolution of mating strategies, targeting our focus on traits affecting inbreeding and polyandry allows us to better isolate their effects and therefore better develop general hypotheses. Future models could be further developed to include additional benefits and costs of reproductive strategies, and benefit and cost values could be parameterised using data from empirical populations, hence enabling more quantitative predictions for specific systems. The addition of such mechanistic detail, and the inclusion of data from populations of interest to parameterise model extensions, could ultimately improve understanding and prediction of reproductive strategy evolution and thereby link theory, modelling, and empirical hypothesis testing.
